How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-03-24 tse-paper/content.tex
Include updated numbers

\section{Systematic Literature Survey}
\label{sec:survey}
% TODO (Caro): Integrate Kitchenham's guidelines
From our own experience, we know that the field of analyzing build
logs is relatively young, with perhaps the work on TravisTorrent the
most cited and central one. We also know there have been scattered
research efforts on build log analysis prior to it, mostly where the
log analysis was a side-part of the article. To the best of our
knowledge, there has not been an attempt to systematically overview
and survey them, despite their forseeable future and current practical
importance.

\subsection{Selection Protocol}
In this first overview, we therefore want to survey as broad a
population of scientific material as possible. Note that we do not
limit our sources to a handful of Software Engineering venues, as is
often done, but survey all sources monitored by Google Scholar,
including Bachelor's and Master's theses, academic slide decks, adn
books. One challenge is that no common nomenclature has been
established yet (in fact, this is one of the goals of this article).

@@

We did a second filter phase by downloading the remaining papers,
reading their abstracts, and searching the full text for the
occurrence of ``log''. If these papers contained traces of working
with build logs, we included them in our survey.

%todo: fill-in number
Wtih these X remaining articles, we followed a backward snowball
sampling for other related work referenced in the paragraphs that
mention the technique. This added four papers (five before duplicate
elimination) to our literature set.

>>>>

\section{Systematic Literature Survey and Mapping}
\label{sec:survey}
% TODO (Caro): Integrate Kitchenham's guidelines
From our own experience, we know that the field of analyzing build
logs is relatively young, with perhaps the work on TravisTorrent the
most cited and central one. We also know there have been scattered
research efforts on build log analysis prior to it, mostly where the
log analysis was a side-part of the article. To the best of our
knowledge, there has not been an attempt to systematically overview
and survey them, despite their forseeable future and current practical
importance.

\subsection{Selection Protocol}
In this first overview, we therefore want to survey as broad a
population of scientific material as possible. Note that we do not
limit our sources to a handful of Software Engineering venues, as is
often done, but survey all sources monitored by Google Scholar,
including Bachelor's and Master's theses, academic slide decks, and
books. We use Google Scholar as opposed to Scopus or other databases,
as it is the search engine for acdemic articles with the broadest and
most current index, including preprints from sources such as
arXiv. One challenge is that no common nomenclature has been
established yet (in fact, this is one of the goals of this article).

@@

Wtih these 259 remaining articles, we followed a backward snowball
sampling for related work. This added three papers (five before
duplicate elimination) to our literature set, coming to a total of 261
articles.

On the 261 artciles, We did a second filter phase by downloading the
surviving papers, reading their abstracts, and searching the full text
for the occurrence of ``log''. If these papers showed even traces of
working with build logs, we included them in our survey. For the
snowballed set, we included two of the three articles, both of which
stem from the same first author, were borderline-includes, and had
called build logs from the Linux kernel ``build traces.'' In total, we
were left with 90 articles after this search.
